%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Timur Sazon} \\ \vspace{1pt}
    \small Philadelphia, PA $|$ 347-598-3198 $|$ \href{mailto:contact@timsazon.dev}{\underline{contact@timsazon.dev}} $|$ 
    \href{https://linkedin.com/in/timsazon}{\underline{linkedin.com/in/timsazon}} $|$
    \href{https://github.com/timsazon}{\underline{github.com/timsazon}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Aug. 2021 -- Feb. 2024}
      {PandaDoc}{Remote (United States)}
      \resumeItemListStart
        \resumeItem{Designed and implemented a new integration platform and collaborated with partner companies on various topics}
        \resumeItem{Owned several critical microservices related to electronic signature and PDF processing}
        \resumeItem{Developed and improved the company's public API}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Oct. 2019 -- Aug. 2021}
      {Sperasoft (Jagex)}{Saint Petersburg, Russia}
      \resumeItemListStart
        \resumeItem{Responsible for system design and implementation of a game publishing platform from scratch}
        \resumeItem{Designed and implemented system security architecture based on Zero Trust standards}
        \resumeItem{Assisted video game developers with a game release on Steam and Twitch integration}
        \resumeItem{Developed various common Java microservice libraries to accelerate development processes in the team}
        \resumeItem{Contributed to open-source OAuth 2.0 libraries to improve tracing capabilities}
    \resumeItemListEnd

    \resumeSubheading
      {Full Stack Software Engineer}{Oct. 2018 -- Oct. 2019}
      {Sperasoft (Sony Interactive Entertainment)}{Volgograd, Russia}
      \resumeItemListStart
        \resumeItem{Designed and implemented a configurable dashboard for data monitoring using React, NodeJS, MongoDB, and Elasticsearch}
        \resumeItem{Developed a system for real time video traffic analysis and detecting playback issues in video streams}
        \resumeItem{Implemented a monitoring and control network bandwidth system, using a set of microservices in Java and front-end in Bootstrap.js and jQuery}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Sep. 2017 -- Oct. 2018}
      {Lecho}{Volgograd, Russia}
      \resumeItemListStart
        \resumeItem{Integrated a payment acquiring system and developed a set of microservices for payments}
        \resumeItem{Developed a CRM platform using Activiti BPMN framework and Spring Boot}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Arma Community Server} $|$ \emph{C++, SQF, C\#}}{}
          \resumeItemListStart
            \resumeItem{Designed and implemented a game launcher with mod download and validation features using .NET Core}
            \resumeItem{Developed game addons using SQF and C++}
            \resumeItem{Hosted a popular game server and website, configured Anti-DDoS protection, and developed game integration services}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Go, Python, JavaScript/TypeScript, C\#, C++} \\
     \textbf{Databases}{: Postgres, MySQL, Redis, MongoDB, AWS DynamoDB, Cassandra, Elasticsearch} \\
     \textbf{Frameworks}{: Spring Boot/MVC, Django, React, NodeJS} \\
     \textbf{Other}{: Git, Docker, Kubernetes (Google Cloud Platform, Amazon Web Services), Terraform, OAuth 2.0 standards}
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Volgograd State University}{Volgograd, Russia}
      {Computer Science}{Sep. 2015 -- May 2019}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
